---
title: "Descriptives of Cancelled Appointments Table"
output: html_notebook
---

```{r}

library(here)
library(tidyverse)
library(kableExtra)

data <- read_rds(here("Generated data","data_with_correct_summary_cancellation_variables.rds")) %>%
  select(starts_with(c("record_id","Any_")))
  

```


# Counts of Screening Cancellations Among Those With Self-Cancellations

## Create tibble of self-cancellation data

```{r}

self_cancelled_table <-
data %>%
  select(record_id, starts_with("Any_Self_Cancelled"), starts_with("Any_Cancer_Screening_Cancellations")) %>%
  
  # pivot to tidy
  pivot_longer(cols = Any_Self_Cancelled_Appt_T1:Any_Cancer_Screening_Cancellations_T3,
               names_to = c('Type','Timepoint'),
               names_pattern = "(.*)_T(.)",
               values_transform = list(value = as.character)
              ) %>%
  
  # pivot to long by timpeoint and participant, wide by type of cancellation (any vs screening)
    pivot_wider(names_from = Type) %>%
  mutate(across(everything(), as.factor))   %>%
  mutate(`Had Self Cancelled Screening` = 
           fct_explicit_na(fct_collapse(Any_Cancer_Screening_Cancellations,
                                        Yes = "Yes:Me",
                                        No = c( "No:(Missing)","Not sure:(Missing)",
                                                "Yes:My healthcare provider","I did not have anything scheduled:(Missing)")), na_level = "No"))

```


## Create summary table of counts of self-cancellations

```{r}

counts_of_self_cancellations <- self_cancelled_table %>%
  count(Timepoint, Any_Self_Cancelled_Appt, `Had Self Cancelled Screening`) %>%
  group_by(Timepoint)%>%
    filter(!is.na(Any_Self_Cancelled_Appt)) %>%
   summarize(Any_Self_Cancelled_Appt = Any_Self_Cancelled_Appt,
     `Had Self Cancelled Screening` = `Had Self Cancelled Screening`,
            n = n,
            `Number Participants With Self-Cancelled Anything At This Timepoint` = sum(n),
    percentage = n / sum(n)) %>%
  mutate(`Percentage to Report` = round(percentage * 100,2)) %>%
  filter(Any_Self_Cancelled_Appt == TRUE)


```

## Plot counts

```{r}

counts_of_self_cancellations %>%
  ggplot() +
  stat_summary(aes(x = Timepoint, y = `Percentage to Report`, fill = `Had Self Cancelled Screening`),
    geom = "bar") +
  ylim(0,100)




```




# Counts of Screening Cancellations Among Those With Provider Cancellations

## Create tibble of provider cancellation data

```{r}

Provider_cancelled_table <-
data %>%
  select(record_id, starts_with("Any_Provider_Cancelled"), starts_with("Any_Cancer_Screening_Cancellations")) %>%
  pivot_longer(cols = Any_Provider_Cancelled_Appt_T1:Any_Cancer_Screening_Cancellations_T3,
               names_to = c('Type','Timepoint'),
               names_pattern = "(.*)_T(.)",
               values_transform = list(value = as.character)
              ) %>%
    pivot_wider(names_from = Type) %>%
  mutate(across(everything(), as.factor))   %>%
  mutate(`Had Provider Cancelled Screening` = 
           fct_explicit_na(fct_collapse(Any_Cancer_Screening_Cancellations,
                                        Yes = "Yes:My healthcare provider",
                                        No = c("No:(Missing)","Not sure:(Missing)",
                                               "Yes:Me","I did not have anything scheduled:(Missing)")), na_level = "No"))

```


## Create summary table of counts of provider cancellations

```{r}

counts_of_Provider_cancellations <- Provider_cancelled_table %>%
  count(Timepoint, Any_Provider_Cancelled_Appt, `Had Provider Cancelled Screening`) %>%
  group_by(Timepoint)%>%
    filter(!is.na(Any_Provider_Cancelled_Appt)) %>%
   summarize(Any_Provider_Cancelled_Appt = Any_Provider_Cancelled_Appt,
     `Had Provider Cancelled Screening` = `Had Provider Cancelled Screening`,
            n = n,
            `Number Participants With Provider Cancelled Anything At This Timepoint` = sum(n),
    percentage = n / sum(n)) %>%
  mutate(`Percentage to Report` = round(percentage * 100,2)) %>%
  filter(Any_Provider_Cancelled_Appt == TRUE)

counts_of_Provider_cancellations 

```

## Plot counts

```{r}

counts_of_Provider_cancellations %>%
  ggplot() +
  stat_summary(aes(x = Timepoint, y = `Percentage to Report`, fill = `Had Provider Cancelled Screening`),
    geom = "bar") +
  ylim(0,100)




```





# Counts of any provider cancellations


## Print counts
```{r}

Provider_cancelled_table %>%
  count(Timepoint, Any_Provider_Cancelled_Appt, Any_Cancer_Screening_Cancellations) %>%
  group_by(Timepoint, Any_Provider_Cancelled_Appt) %>%
    filter(!is.na(Any_Provider_Cancelled_Appt)) %>%
   summarize(Any_Cancer_Screening_Cancellations = Any_Cancer_Screening_Cancellations,
            n = n,
            `Number Participants With Provider-Cancelled Anything At This Timepoint` = sum(n),
    percentage = n / sum(n)) %>%
  mutate(`Percentage to Report` = round(percentage * 100,2)) %>%
  filter(Any_Provider_Cancelled_Appt == TRUE)# %>%
  #filter(Any_Cancer_Screening_Cancellations == "Yes:My healthcare provider")

```

# Combine Self- and Provider Cancelled Data

## Setup count tables

```{r}

counts_of_self_cancellations.combine <- counts_of_self_cancellations %>%
  mutate(type = 'Self-Cancellation') %>%
  rename(`Had Self/Provider Cancelled Screening` = `Had Self Cancelled Screening`) %>%
  select(Timepoint, `Had Self/Provider Cancelled Screening`, n, `Percentage to Report`, type)

counts_of_provider_cancellations.combine <- counts_of_Provider_cancellations %>%
  mutate(type = 'Provider Cancellation') %>%
  rename(`Had Self/Provider Cancelled Screening` = `Had Provider Cancelled Screening`)  %>%
  select(Timepoint, `Had Self/Provider Cancelled Screening`, n, `Percentage to Report`, type)

```

```{r}
 combined_data <- bind_rows(counts_of_self_cancellations.combine, counts_of_provider_cancellations.combine ) %>%
  
  
  mutate(
    # rename timepoints to be more informative
    Timepoint = forcats::fct_recode(Timepoint, 
                                         "May 2020" = "1",
                                         "June/July 2020" = "2",
                                         "November 2020" = "3"),
    
    # re-order other factors so they display in desired order in plot
    
    #`Had Self/Provider Cancelled Screening` = fct_relevel(`Had Self/Provider Cancelled Screening`, "Yes"),
    type = forcats::fct_relevel(type, "Self-Cancellation")) %>%
  
  # rename levels of this variable so that they display on plot
  mutate(type = forcats::fct_recode(type, 
                                         "Participants with Self-Cancellation(s)" = "Self-Cancellation",
                                    "Participants with Provider Cancellation(s)" = "Provider Cancellation"))



```
## Plot

```{r}
combined_plot <- 
combined_data %>%
    ggplot() +
  stat_summary(aes(x = Timepoint, y = `Percentage to Report`, fill = `Had Self/Provider Cancelled Screening`),
    geom = "bar")  +
  scale_fill_manual(values = c("grey","black")) +
  ylim(0, 100) +
  ylab('%') +
  theme_minimal() +
  xlab('') +
  theme(legend.position = 'bottom') +
  facet_grid(cols = vars(type)) +
    theme(strip.text.y = element_text(angle = 0))

combined_plot 
```

## Save plot

```{r}

ggplot2::ggsave(plot = combined_plot, filename = here('Plots','Counts of Cancellations Plot.jpg'), dpi = 300,  width = 7, height = 5, units = "in")

```
