---
title: "Run McNemar's test and print contingency tables"
output:
  html_document:
    df_print: paged
  html_notebook: default
  word_document: default
  pdf_document: default
---

Purpose: run McNemar's tests to compare provider and self-cancelled screenings and appointments at different timepoints.

```{r include=FALSE}
library(tidyverse)
library(here)
library(kableExtra)
library(pander)

```


```{r include=FALSE}
  
data <- read_rds(here("Generated data","data_with_correct_summary_cancellation_variables.rds"))
  
```

# Generic function for formatting the data correctly and running McNemar's test

Approach to set up McNemar's test with table() used here is adapted from https://www.r-bloggers.com/2021/06/paired-test-for-dichotomous-data-mcnemars-test-in-r/

```{r}

setupMcNemarsTest <- function(var1, var2) {
  
  # remove cases with missing data at either timepoint
  my_data <- tibble(var1, var2) %>%
    filter(!is.na(var1)) %>%
    filter(!is.na(var2))
  
  
  
  data_table <- table(my_data$var1, my_data$var2)
  
  return(data_table)
  
}


printContingencyTable <- function(var1, var2, self_or_provider, screening_or_appointment) {
  
  true_text <- str_c("Had ", self_or_provider ,"-cancelled ", screening_or_appointment)
  false_text <- str_c("No ", self_or_provider ,"-cancelled ", screening_or_appointment)
  
  # get counts
  tibble(var1, var2) %>%
    mutate(participant = c(1:length(var1))) %>%
    count(var1, var2) %>%
    
    # remove cases with missing data at either timepoint
    filter(!is.na(var1) & !is.na(var2)) %>%
    
    # create N (%) table
    mutate(`%` = finalfit::round_tidy(100*(n/sum(n)),2)) %>%
    mutate(`N (%)` = str_c(n, ' (',`%`,"%",')')) %>%
    
    # clean up output so that it looks like a contingency table
    select(-n, -`%`) %>%
    arrange(-var1, -var2) %>%
    pivot_wider(values_from = `N (%)`, names_from = var2) %>%
    
    # rename TRUE/FALSE
    mutate(var1 = ifelse(var1 == TRUE, true_text,false_text)) %>%
    
    # print in html
    kableExtra::kable(col.names = c(' ',true_text,false_text)) %>%
    kableExtra::kable_classic(html_font = 'Times New Roman', full_width=FALSE) %>%
    group_rows(group_label = 'Time Var1', start_row = 1, end_row = 2, bold = FALSE) %>%
    kableExtra::add_header_above(c(" " = 1, 'Time Var2' = 2 )) %>%
    
    return()
}
    
```



# Self cancelled appts

## ANY Appt

### T1 with T2

```{r echo=FALSE}

setupMcNemarsTest(data$Any_Self_Cancelled_Appt_T1, data$Any_Self_Cancelled_Appt_T2) %>%
  mcnemar.test()

 
printContingencyTable(data$Any_Self_Cancelled_Appt_T1, data$Any_Self_Cancelled_Appt_T2,
                    self_or_provider = "self",
                    screening_or_appointment =  "appointment(s)")
```


### T2 with T3

```{r echo=FALSE}

setupMcNemarsTest(data$Any_Self_Cancelled_Appt_T2, data$Any_Self_Cancelled_Appt_T3) %>%
  mcnemar.test()

printContingencyTable(data$Any_Self_Cancelled_Appt_T2, data$Any_Self_Cancelled_Appt_T3,
                    self_or_provider = "self",
                    screening_or_appointment =  "appointment(s)")
```

### T1 with T3

```{r echo=FALSE}

setupMcNemarsTest(data$Any_Self_Cancelled_Appt_T1, data$Any_Self_Cancelled_Appt_T3) %>%
  mcnemar.test()

printContingencyTable(data$Any_Self_Cancelled_Appt_T1, data$Any_Self_Cancelled_Appt_T3,
                    self_or_provider = "self",
                    screening_or_appointment =  "appointment(s)")
```



## SCREENING


### T1 with T2

```{r echo=FALSE}

table(data$Any_Self_Cancelled_Screening_T1)

setupMcNemarsTest(data$Any_Self_Cancelled_Screening_T1, data$Any_Self_Cancelled_Screening_T2) %>%
  mcnemar.test()
 
printContingencyTable(data$Any_Self_Cancelled_Screening_T1, data$Any_Self_Cancelled_Screening_T2,
                    self_or_provider = "self",
                    screening_or_appointment =  "screening(s)")
```


### T2 with T3

```{r echo=FALSE}

table(data$Any_Self_Cancelled_Screening_T2)

setupMcNemarsTest(data$Any_Self_Cancelled_Screening_T2, data$Any_Self_Cancelled_Screening_T3) %>%
  mcnemar.test()
 
printContingencyTable(data$Any_Self_Cancelled_Screening_T2, data$Any_Self_Cancelled_Screening_T3,
                    self_or_provider = "self",
                    screening_or_appointment =  "screening(s)")
```

### T1 with T3

```{r echo=FALSE}

setupMcNemarsTest(data$Any_Self_Cancelled_Screening_T1, data$Any_Self_Cancelled_Screening_T3) %>%
  mcnemar.test()
 
printContingencyTable(data$Any_Self_Cancelled_Screening_T1, data$Any_Self_Cancelled_Screening_T3,
                    self_or_provider = "self",
                    screening_or_appointment =  "screening(s)")
```



# Provider cancelled appts
## T1 with T2

```{r echo=FALSE}

setupMcNemarsTest(data$Any_Provider_Cancelled_Appt_T1, data$Any_Provider_Cancelled_Appt_T2) %>%
  mcnemar.test()

printContingencyTable(data$Any_Provider_Cancelled_Appt_T1, data$Any_Provider_Cancelled_Appt_T2,
                    self_or_provider = "provider",
                    screening_or_appointment =  "appointment(s)")

```


## T2 with T3

```{r echo=FALSE}

setupMcNemarsTest(data$Any_Provider_Cancelled_Appt_T2, data$Any_Provider_Cancelled_Appt_T3) %>%
  mcnemar.test()

printContingencyTable(data$Any_Provider_Cancelled_Appt_T2, data$Any_Provider_Cancelled_Appt_T3,
                    self_or_provider = "provider",
                    screening_or_appointment =  "appointment(s)")

```

## T1 with T3

```{r echo=FALSE}

setupMcNemarsTest(data$Any_Provider_Cancelled_Appt_T1, data$Any_Provider_Cancelled_Appt_T3) %>%
  mcnemar.test()

printContingencyTable(data$Any_Provider_Cancelled_Appt_T1, data$Any_Provider_Cancelled_Appt_T3,
                    self_or_provider = "provider",
                    screening_or_appointment =  "appointment(s)")

```




## SCREENING


### T1 with T2

```{r echo=FALSE}

setupMcNemarsTest(data$Any_Provider_Cancelled_Screening_T1, data$Any_Provider_Cancelled_Screening_T2) %>%
  mcnemar.test()
 
printContingencyTable(data$Any_Provider_Cancelled_Screening_T1, data$Any_Provider_Cancelled_Screening_T2,
                    self_or_provider = "provider",
                    screening_or_appointment =  "screening(s)")
```


### T2 with T3

```{r echo=FALSE}

table(data$Any_Provider_Cancelled_Screening_T2)

setupMcNemarsTest(data$Any_Provider_Cancelled_Screening_T2, data$Any_Provider_Cancelled_Screening_T3) %>%
  mcnemar.test()
 
printContingencyTable(data$Any_Provider_Cancelled_Screening_T2, data$Any_Provider_Cancelled_Screening_T3,
                    self_or_provider = "provider",
                    screening_or_appointment =  "screening(s)")
```

### T1 with T3

```{r echo=FALSE}

setupMcNemarsTest(data$Any_Provider_Cancelled_Screening_T1, data$Any_Provider_Cancelled_Screening_T3) %>%
  mcnemar.test()
 
printContingencyTable(data$Any_Provider_Cancelled_Screening_T1, data$Any_Provider_Cancelled_Screening_T3,
                    self_or_provider = "provider",
                    screening_or_appointment =  "screening(s)")


```