---
title: "Combine Variables for Missed Appointments"
output: html_notebook
---

# Read in libraries and data

```{r}
library(tidyverse)
library(here)
library(pander)

data_all <- read_csv(file = '~/On HD/Raw data/Covid study/COVID Main Database All_07-8-21.csv')
  

```

# Create missed appointment variables

We are going to combine four variables to look at any self-cancelled appts or any provider-cancelled appts:

* Self-cancelled appts (screening or any other kind of appt)*

Variables:
1. adh_cancer_test_who: Who postponed or cancelled your routine cancer screening? Count "Me" answers as self-cancelled screening apts
2. adh_cancer_you: Over the last 2 months have you cancelled or postponed scheduled visits or services for physical health or mental health?


* Provider-cancelled appts (screening or any other kind of appt)*

Variables:
1. adh_cancer_test_who: Who postponed or cancelled your routine cancer screening? Count "My provider" answers as provider-cancelled screening apts
2. adh_cancer_apt: Over the last 2 months, have any of your healthcare providers cancelled or postponed scheduled visits or services for physical or mental health?


```{r}


data_to_export <- 
  data_all %>%
  
  # create factor variables out of existing variables
  #Over the last 2 months, have any of your healthcare providers cancelled or postponed scheduled visits or services for physical or mental health?
  
  mutate(adh_cancer_apt_T1 = factor(adh_cancer_apt_T1,
                                         levels = c(0,1,2,3),
                                         labels = c('No','Yes','Not Sure', 'I did not have anything scheduled')),
         adh_cancer_apt_T2 = factor(adh_cancer_apt_T2,
                                         levels = c(0,1,2,3),
                                         labels = c('No','Yes','Not Sure', 'I did not have anything scheduled')),
         adh_cancer_apt_T3 = factor(adh_cancer_apt_T3,
                                         levels = c(0,1,2,3),
                                         labels = c('No','Yes','Not Sure', 'I did not have anything scheduled')),
  
  # this variable has flipped labels for levels 2 and 3 compared to prior variables
  # Over the last 2 months, have you or your healthcare provider cancelled or postponed getting routine cancer screening (breast cancer mammography, colonoscopy, pap smear etc.)?
  
         adh_cancer_test_T1 = factor(adh_cancer_test_T1,
                                     levels = c(0,1,2,3),
                                       labels = c('No','Yes', 'Not sure', 'I did not have anything scheduled')),
                  adh_cancer_test_T2 = factor(adh_cancer_test_T2,
                                     levels = c(0,1,2,3),
                                       labels = c('No','Yes', 'Not sure', 'I did not have anything scheduled')),
                  adh_cancer_test_T3 = factor(adh_cancer_test_T3,
                                     levels = c(0,1,2,3),
                                    labels = c('No','Yes', 'Not sure', 'I did not have anything scheduled')),
        
  #Over the last 2 months have you cancelled or postponed scheduled visits or services for physical health or mental health?
   adh_cancer_you_T1 = factor(adh_cancer_you_T1,
                                         levels = c(0,1,2,3),
                                         labels = c('No','Yes','Not Sure', 'I did not have anything scheduled')),
         adh_cancer_you_T2 = factor(adh_cancer_you_T2,
                                         levels = c(0,1,2,3),
                                         labels = c('No','Yes','Not Sure', 'I did not have anything scheduled')),
         adh_cancer_you_T3 = factor(adh_cancer_you_T3,
                                         levels = c(0,1,2,3),
                                         labels = c('No','Yes','Not Sure', 'I did not have anything scheduled')),
    adh_cancer_test_who_T1 = fct_explicit_na(factor(adh_cancer_test_who_T1,
                                         levels = c(1,2),
                                         labels = c('Me','My healthcare provider'))),
         adh_cancer_test_who_T2 = fct_explicit_na(factor(adh_cancer_test_who_T2,
                                         levels = c(1,2),
                                         labels = c('Me','My healthcare provider'))),
         adh_cancer_test_who_T3 = fct_explicit_na(factor(adh_cancer_test_who_T3,
                                         levels = c(1,2),
                                         labels = c('Me','My healthcare provider'))),
  
  Any_Cancer_Screening_Cancellations_T1 = fct_cross(adh_cancer_test_T1, adh_cancer_test_who_T1),
  Any_Cancer_Screening_Cancellations_T2 = fct_cross(adh_cancer_test_T2, adh_cancer_test_who_T2),
  Any_Cancer_Screening_Cancellations_T3 = fct_cross(adh_cancer_test_T3, adh_cancer_test_who_T3)) %>%
  
  # create new variables, which are self-cancelled cancer screenings (T/F at each timepoint) and provider-cancelled screenings (T/F at each timepoint)
  mutate(Any_Self_Cancelled_Screening_T1 = ifelse(Any_Cancer_Screening_Cancellations_T1 == "Yes:Me", TRUE, FALSE),
         Any_Self_Cancelled_Screening_T2 = ifelse(Any_Cancer_Screening_Cancellations_T2 == "Yes:Me", TRUE, FALSE),
         Any_Self_Cancelled_Screening_T3 = ifelse(Any_Cancer_Screening_Cancellations_T3 == "Yes:Me", TRUE, FALSE),
         
         Any_Provider_Cancelled_Screening_T1 = ifelse(Any_Cancer_Screening_Cancellations_T1 == "Yes:My healthcare provider", TRUE, FALSE),
         Any_Provider_Cancelled_Screening_T2 = ifelse(Any_Cancer_Screening_Cancellations_T2 == "Yes:My healthcare provider", TRUE, FALSE),
         Any_Provider_Cancelled_Screening_T3 = ifelse(Any_Cancer_Screening_Cancellations_T3 == "Yes:My healthcare provider", TRUE, FALSE)) %>%
  
  # create missed appointment variables
  mutate(Any_Self_Cancelled_Appt_T1 = (adh_cancer_you_T1 == "Yes" | Any_Cancer_Screening_Cancellations_T1 == "Yes:Me"),
         Any_Self_Cancelled_Appt_T2 = (adh_cancer_you_T2 == "Yes" | Any_Cancer_Screening_Cancellations_T2 == "Yes:Me"),
         Any_Self_Cancelled_Appt_T3 = (adh_cancer_you_T3 == "Yes" | Any_Cancer_Screening_Cancellations_T3== "Yes:Me"),
         Any_Provider_Cancelled_Appt_T1 = (adh_cancer_apt_T1 == "Yes" | Any_Cancer_Screening_Cancellations_T1 == "Yes:My healthcare provider"),
         Any_Provider_Cancelled_Appt_T2 = (adh_cancer_apt_T2 == "Yes" | Any_Cancer_Screening_Cancellations_T2 == "Yes:My healthcare provider"),
         Any_Provider_Cancelled_Appt_T3 = (adh_cancer_apt_T3 == "Yes" | Any_Cancer_Screening_Cancellations_T3== "Yes:My healthcare provider"))
  

```



## Export for joel

```{r}

write_rds(data_to_export, here("Generated data","data_with_correct_summary_cancellation_variables.rds"))

```



