---
title: "Raw scores of covariates at each timepoint"
output:
  html_document:
    df_print: paged
  html_notebook: default
  pdf_document: default
---

Purpose: For revise and resubmit, per reviewer request, compute scores of each regression model covariate at each timepoint

```{r}
library(tidyverse)
library(here)
library(pander)

data <- read_rds(file = here("Generated data","data_with_correct_summary_cancellation_variables.rds"))

data %>%
    select(record_id, 
         starts_with("gad7_tot_T"), 
         starts_with("phq8_tot_T"), 
         starts_with("cfi_mean_T"),
         starts_with("cfi_survivor_mean_T")) 
```


```{r}

data.long <- data %>%
  select(record_id, 
         starts_with("gad7_tot_T"), 
         starts_with("phq8_tot_T"), 
         starts_with("cfi_mean_T"),
         starts_with("cfi_survivor_mean_T"))   %>%
  pivot_longer(cols = gad7_tot_T1:cfi_survivor_mean_T3,
               names_pattern = "(.*)_T(.)",
               names_to = c("variable","timepoint"))



```

# Check that long and wide datasets match up as expected

Looks good on 6/3/22

```{r}

data %>%
    select(record_id, 
         starts_with("gad7_tot_T"), 
         starts_with("phq8_tot_T"), 
         starts_with("cfi_mean_T"),
         starts_with("cfi_survivor_mean_T")) %>%
  
  filter(record_id == 6)

```


```{r}
data.long %>%
  filter(record_id == 6)

```
# Compute summary statistics

```{r}

data.long %>%
  group_by(variable, timepoint) %>%
  summarise(mean = mean(value, na.rm = TRUE),
            sd = sd(value, na.rm = TRUE)) %>%
  mutate(across(.cols = mean:sd, round, 2)) %>%
  kableExtra::kable() %>%
  kableExtra::kable_classic(full_width = FALSE, html_font = "Times New Roman")
```



# Display scores graphically

NOTE TO LAUREN: We may not actually want to display the data this way but I increasingly like displays like this as opposed to summary stats. They give you a full sense of the range and how the range and distribution change over time. If you and Joanna like this display I can clean it up with better variable names, etc.

Black dot indicates mean, thick black line indicates 67% quantile, thin black line indicates 95% quantile.

```{r}

data.long %>%
  ggplot(aes(x = value)) +
  ggdist::stat_dotsinterval() +
  facet_grid(timepoint ~ variable, scales = 'free_x')
  
```