---
title: "Regression Models"
output: html_document
---

# Read in libraries and data

```{r}

library(psych)
library(here)
library(tidyverse)

data <-  read_csv(file = here('Raw Data','COVID Main Database All_07-8-21.csv'))


```

# Single predictor models

## Timepoint 1

```{r}
#Anxiety
anxiety1 <- glm(Any_Self_Cancelled_Appt_T1 ~ gad7_tot_T1, data=data, family=binomial)

#Depression
dep1 <- glm(Any_Self_Cancelled_Appt_T1 ~ phq8_tot_T1, data=data, family=binomial)

#General COVID fears
fear1 <- glm(Any_Self_Cancelled_Appt_T1 ~ cfi_mean_T1, data=data, family=binomial)

#Cancer-specific COVID fears
canc_fear1 <- glm(Any_Self_Cancelled_Appt_T1 ~ cfi_survivor_mean_T1, data=data, family=binomial)
```

## Timepoint 2
```{r}
anxiety2 <- glm(Any_Self_Cancelled_Appt_T2 ~ gad7_tot_T2, data=data, family=binomial)
dep2 <- glm(Any_Self_Cancelled_Appt_T2 ~ phq8_tot_T2, data=data, family=binomial)
fear2 <- glm(Any_Self_Cancelled_Appt_T2 ~ cfi_mean_T2, data=data, family=binomial)
canc_fear2 <- glm(Any_Self_Cancelled_Appt_T2 ~ cfi_survivor_mean_T2, data=data, family=binomial)
```

## Timepoint 3
```{r}
anxiety3 <- glm(Any_Self_Cancelled_Appt_T3 ~ gad7_tot_T3, data=data, family=binomial)
dep3 <- glm(Any_Self_Cancelled_Appt_T3 ~ phq8_tot_T3, data=data, family=binomial)
fear3 <- glm(Any_Self_Cancelled_Appt_T3 ~ cfi_mean_T3, data=data, family=binomial)
canc_fear3 <- glm(Any_Self_Cancelled_Appt_T3 ~ cfi_survivor_mean_T3, data=data, family=binomial)

```

# Multivariate

Anxiety and depression not included in the same models because they are too closely correlated...we observed issues with multicollinearity when including both phq8_tot and gad7_tot in the same models

## Depression, general covid fears, and cancer-specific covid fears

```{r}
multivariate.depression.T1.fit <- glm(Any_Self_Cancelled_Appt_T1 ~ phq8_tot_T1 + cfi_mean_T1 + cfi_survivor_mean_T1, data=data, family=binomial)

multivariate.depression.T2.fit <- glm(Any_Self_Cancelled_Appt_T2 ~ phq8_tot_T2 + cfi_mean_T2 + cfi_survivor_mean_T2, data=data, family=binomial)

multivariate.depression.T3.fit <- glm(Any_Self_Cancelled_Appt_T3 ~ phq8_tot_T3 + cfi_mean_T3 + cfi_survivor_mean_T3, data=data, family=binomial)

```

## Anxiety, general covid fears, and cancer-specific covid fears

```{r}
multivariate.anxiety.T1.fit <- glm(Any_Self_Cancelled_Appt_T1 ~ gad7_tot_T1 + cfi_mean_T1 + cfi_survivor_mean_T1, data=data, family=binomial)

multivariate.anxiety.T2.fit <- glm(Any_Self_Cancelled_Appt_T2 ~ gad7_tot_T2 + cfi_mean_T2 + cfi_survivor_mean_T2, data=data, family=binomial)

multivariate.anxiety.T3.fit <- glm(Any_Self_Cancelled_Appt_T3 ~ gad7_tot_T3 + cfi_mean_T3 + cfi_survivor_mean_T3, data=data, family=binomial)


```




# Save model fits

```{r}

write_rds(anxiety1, here('Model fits','anxiety1.rds'))
write_rds(anxiety2, here('Model fits','anxiety2.rds'))
write_rds(anxiety3, here('Model fits','anxiety3.rds'))

write_rds(dep1, here('Model fits','dep1.rds'))
write_rds(dep2, here('Model fits','dep2.rds'))
write_rds(dep3, here('Model fits','dep3.rds'))


write_rds(fear1, here('Model fits','fear1.rds'))
write_rds(fear2, here('Model fits','fear2.rds'))
write_rds(fear3, here('Model fits','fear3.rds'))

write_rds(canc_fear1, here('Model fits','canc_fear1.rds'))
write_rds(canc_fear2, here('Model fits','canc_fear2.rds'))
write_rds(canc_fear3, here('Model fits','canc_fear3.rds'))

write_rds(multivariate.depression.T1.fit, here('Model fits','multivariate.depression.T1.fit.rds'))
write_rds(multivariate.depression.T2.fit, here('Model fits','multivariate.depression.T2.fit.rds'))
write_rds(multivariate.depression.T3.fit, here('Model fits','multivariate.depression.T3.fit.rds'))

write_rds(multivariate.anxiety.T1.fit, here('Model fits','multivariate.anxiety.T1.fit.rds'))
write_rds(multivariate.anxiety.T2.fit, here('Model fits','multivariate.anxiety.T2.fit.rds'))
write_rds(multivariate.anxiety.T3.fit, here('Model fits','multivariate.anxiety.T3.fit.rds'))

```


